Why Donors Donate?

### 2020-09-02 analysis/05_market_simulator.Rmd
format change
Recoding some input levels

# Need to Fix
selectInput("p1_worship_attendance",
         label = "Worship service attendance:",
         choices = c('Multiple times a week',
                     'Once a week',
                     "Once a month",
                     "Once a year",
                     "Never"))

@@

# Need to Fix
selectInput("p1_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c('Once a week',
                     'Once a Month',
                     'Once every three months',
                     'Once every six months',
                     'Once a year',
                     'Once every few years',
                     'Never'))

>>>>

# Need to Fix
selectInput("p1_worship_attendance",
         label = "Worship service attendance:",
         choices = c('Multiple times a week',
                     'Once a week',
                     "Once a month",
                     "Few times a year",
                     "Once a year",
                     "Never"))

@@

# Need to Fix
selectInput("p1_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c('Once a week',
                     'Once a Month',
                     'Once every three months',
                     'Once every six months',
                     'Once a year',
                     'Once every few years'))
